paper

### 2021-10-07 paper.Rmd
AS
as

```{r}
new_dt <- 
  data %>% 
  rename (herbicide = other) %>% 
  mutate(
    wt_14 = waterhempcontrol_14/100,
    wt_28 = waterhempcontrol_28/100,
    yield_kg = yield_bu * 67.5) %>% 
  mutate(
    wt_14 = 
      case_when(
        waterhempcontrol_14 == 100   ~  0.99,
        TRUE            ~ wt_14),
    wt_28 = case_when(
        waterhempcontrol_28 == 100   ~  0.99,
        waterhempcontrol_28 == 0   ~  0.01,
        TRUE            ~ wt_28)) %>% 
  filter(
    herbicide != "PRE only"
  ) %>% 
  mutate_if(is_character, as.factor) %>% 
  mutate(rep = as.factor(rep),
         year = as.factor(year))
```

@@

@@

```{r}
epred1_1 %>% 
  bind_rows(epred2_2) %>% 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred_wt
```

@@

ggsave("figures/Figure 3.png", width = 6, height = 4)
```

```{r}
library(patchwork)
```

```{r}
fig1 + fig2

ggsave("figures/Figure 4.png", width = 9)
```

>>>>

```{r}
new_dt <- 
  data %>% 
  rename (herbicide = other) %>% 
  mutate(
    wt_14 = waterhempcontrol_14/100,
    wt_28 = waterhempcontrol_28/100,
    wt_hv = waterhempcontrol_harvest/100,
    yield_kg = yield_bu * 67.5) %>% 
  mutate(
    wt_14 = 
      case_when(
        waterhempcontrol_14 == 100   ~  0.99,
        TRUE            ~ wt_14),
    wt_28 = case_when(
        waterhempcontrol_28 == 100   ~  0.99,
        waterhempcontrol_28 == 0   ~  0.01,
        TRUE            ~ wt_28)) %>% 
  filter(
    herbicide != "PRE only"
  ) %>% 
  mutate_if(is_character, as.factor) %>% 
  mutate(rep = as.factor(rep),
         year = as.factor(year))
```

@@

# Harvest

```{r}
model5 <- brm(wt_hv ~ herbicide +
                (1|rep/location/year),
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 11),
               prior = set_prior("student_t(0.1, 0.5, 8)", 
                                 class = "b"),
              seed = 1234,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

```{r}
summary(model5)
```

```{r}
epred5 <- emmeans(model5, "herbicide", epred = TRUE) |> 
  as_tibble() %>% 
  mutate(DAT = "Harvest")
```

```{r}
whv_main <- pairs(emmeans(model5, ~ herbicide))

describe_posterior(whv_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model5)
```

@@

```{r}
epred1_1 %>% 
  bind_rows(epred2_2) %>% 
  bind_rows(epred5) |> 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred_wt
```

@@

ggsave("figures/Figure 4.png", width = 6, height = 4)
```

## Biomass

```{r}
new_dt |> 
  ungroup() |> 
  dplyr::mutate(location, year, herbicide, rep, biomass_gm2) |> 
  filter(!is.na(biomass_gm2)) -> biomass
```

```{r}
model3 <- brm(biomass_gm2 ~ herbicide +
                (1|rep/location), 
                  family = gaussian(),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 11),
               prior = set_prior("student_t(0.1, 2, 8)", 
                                 class = "b"),
              seed = 1234,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

```{r}
epred3 <- emmeans(model3, "herbicide", epred = TRUE,
                  #cont="pairwise"
                  )
epred3
```

```{r}
biomass_main <- pairs(emmeans(model3, ~ herbicide))

describe_posterior(biomass_main,
                   centrality = "median", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model3)
```

```{r}
mod_3 <- lmer(biomass_gm2 ~ herbicide +
                (1|rep/location),
                  data = new_dt)
```

```{r}
anova(mod_3)
```
